PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-29 paper/paper.tex
Working on paper

\def\eg{\emph{e.g.\/}}
\def\ie{\emph{i.e.\/}}
\def\etc{\emph{etc.\/}}
\def\etal{\emph{et al.\/}}
\DeclareMathOperator*{\median}{median}

@@

\subsection{Segmentation}

Evaluation criteria for segmentation fall into two categories: boundary annotation, and structural annotation.
\emph{Boundary annotation} is the task of predicting the times at which structural changes occur, such as when a \emph{verse} transitions to a \emph{refrain}.
\emph{Structural annotation} is the task of assigning labels to detected segments.  
The estimated labels may be arbitrary strings --- such as $A$, $B$, $C$, \etc{} --- and they need not describe functional concepts.

In both tasks, we assume that annotations take the form of a partitioning of the track 
into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
Structural annotation additionally requires that each interval be assigned a label $y_i$.

\subsubsection{Boundary annotation}

Within boundary annotation, there are two categories of evaluation metrics: detection,
and deviation~\cite{turnbull2007supervised}.

\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
Let $B_R$ ($B_E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
a tolerance window, typically either $0.5$s or $3.0$s.  
A \emph{hit} is defined as a pair $b_e \in B_E$, $b_r \in B_R$ such that $|b_e - b_r|
\leq W$.

To define detection metrics, we require that no estimated boundary is counted for more than one reference boundary, and vice versa.
This is accomplished by computing a maximum bipartite matching $H_W$ between $B_E$ and $B_R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
Precision and recall with window $W$ are defined as
\begin{align}
P_W(B_R, B_E) &:= \frac{|H_W|}{|B_E|}\\
R_W(B_R, B_E) &:= \frac{|H_W|}{|B_R|},
\end{align}
and the corresponding f-measure is defined by taking their harmonic mean.

\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
\begin{align}
\text{R-to-E}(B_R, B_E) &:= \displaystyle\median_{b_r \in B_R} \min_{b_e \in B_E} \left|b_r - b_e\right|\\
\text{E-to-R}(B_R, B_E) &:= \displaystyle\median_{b_e \in B_E} \min_{b_r \in B_R} \left|b_r - b_e\right|.
\end{align}

\subsubsection{Structural annotation}

\subsection{Melody Extraction}
\subsubsection{Task definition}
Melody extraction algorithms aim to produce a sequence of frequency values
corresponding to the pitch of the dominant melody from a musical recording
\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
sequence is generated by running a pitch tracker on the monophonic melody track
(requiring access to the multi-track recording session) and manually correcting
any mistakes made by the pitch tracker. The estimate is then evaluated against
the reference by comparing the two frequency sequences on a frame-by-frame
basis, and computing five global measures, first used in the MIREX 2005 AME
evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
is to assess the algorithm's performance on two subtasks of melody extraction:
(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
melody, and (2) voicing detection, i.e.~how well the algorithm determines when
the melody is present in a frame (a \textit{voiced} frame) or absent (an
\textit{unvoiced} frame). To allow evaluation of these two subtasks
independently, a melody extraction algorithm can provide a frequency estimate
even for frames it has determined to be unvoiced.

\subsubsection{Evaluation measures}
The following definitions are taken from
\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
Then the measures are:
\begin{itemize}
  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
  melody frames in the reference that are estimated as melody frames by the
  algorithm.
\begin{equation}
\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
\end{equation}

  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
  labeled as non-melody in the reference that are mistakenly estimated as
  melody frames by the algorithm.
\begin{equation}
\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
\end{equation}

  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
  reference for which $f_\tau$ is considered
  correct (i.e.~within half a semitone of the ground
  truth $f^*_\tau$).
\begin{equation}
\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
\end{equation}
where $\mathcal{T}$ is a threshold function defined by:
\begin{equation}
\mathcal{T}[a] = \begin{cases}
1 \quad \text{if } |a| < 0.5 \\
0 \quad \text{if } |a| \ge 0.5
\end{cases}
\end{equation}
and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
axis as a real-valued number of semitones above an arbitrary
reference frequency $f_\text{ref}$:
\begin{equation}
\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
\end{equation}

  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
  that both the estimated and reference $f_0$ sequences are mapped onto a
  single octave. This gives a measure of pitch accuracy which ignores octave
  errors, a common error made by melody extraction systems:
\begin{equation}
\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
\end{equation}
Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
values modulo 12 (one octave), where
\begin{equation}
\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
\end{equation}

  \item \textbf{Overall Accuracy}: this measure combines the performance of the
  pitch estimation and voicing detection tasks to give an overall performance
  score for the system. It is defined as the proportion of all frames
   correctly estimated by the algorithm, where for non-melody
  frames this means the algorithm labeled them as non-melody, and for melody
  frames the algorithm both labeled them as melody frames and provided a correct
  $f_0$ estimate for the melody (i.e.~within half a semitone of the
  reference):

\begin{equation}
\text{Acc}_\text{ov} 
= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
\end{equation}
where $L$ is the total number of frames.
\end{itemize}

The performance of an algorithm on an entire music collection for a given
measure is obtained by averaging the per-excerpt scores for that measure over
all excerpts in the collection.

\subsubsection{Discussion}

In the measure definitions provided above, it is assumed that both the estimate
and reference sequences are sampled using the same time grid (hop size). In
practice, however, this is not always the case, since the time grid of the
reference depends on the hop size used by the pitch tracker that produced
it, and similarly the time grid of the estimate depends on the specific melody
extraction algorithm that produced it. This means that the sequences must be
resampled onto a common time-grid prior to the computation of the measures. For
the MIREX AME task, any sequence (be it reference or estimate) that is not
sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
i.e.~each frequency value in the target sequence is set to its nearest
neighbour (in time) from the source sequence. This kind of interpolation can
potentially have a detrimental effect on the evaluation, depending on the
difference between the source and target time grids. In particular, it can
result in artificially low scores for sequences with rapidly changing pitch
values, such as opera singing with deep vibrato.

For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by mir\_eval are lower-bounded by the MIREX results and are, in our
view, more accurate.

% \subsection{Figures, Tables and Captions}
% 
% All artwork must be centered, neat, clean, and legible.
% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
% Figure and table numbers and captions always appear below the figure.
% Leave 1 line space between the figure or table and the caption.
% Each figure or table is numbered consecutively. Captions should be Times 10pt.
% Place tables/figures in text as close to the reference as possible.
% References to tables and figures should be capitalized, for example:
% see \figref{fig:example} and \tabref{tab:example}.
% Figures and tables may extend across both columns to a maximum width of 17.2cm.

% \begin{table}
%  \begin{center}
%  \begin{tabular}{|l|l|}
%   \hline
%   String value & Numeric value \\
%   \hline
%   Hello ISMIR  & 2014 \\
%   \hline
%  \end{tabular}
% \end{center}
%  \caption{Table captions should be placed below the table.}
%  \label{tab:example}
% \end{table}

>>>>

@@

\subsection{Pattern Discovery}

This recent MIREX task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
Given the novelty of this task, the metrics used in 2013 (the first year to appear on MIREX) are subject to modifications in further editions.
However, Colins\cite{TomColins2013} put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX, which resulted in 21 different scores, each one implemented in MIR-eval.

\subsubsection{Third and Further Level Headings}

Third level headings are in Times 10pt italic, flush left,
with 1/2 line of space above the section head, and 1/2 space below it.
The first letter of each significant word is capitalized.

Using more than three levels of headings is highly discouraged.

\section{Footnotes and Figures}

\subsection{Footnotes}

Indicate footnotes with a number in the text.\footnote{This is a footnote.}
Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a 0.5pt horizontal rule.

\subsection{Figures, Tables and Captions}

All artwork must be centered, neat, clean, and legible.
All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
Figure and table numbers and captions always appear below the figure.
Leave 1 line space between the figure or table and the caption.
Each figure or table is numbered consecutively. Captions should be Times 10pt.
Place tables/figures in text as close to the reference as possible.
References to tables and figures should be capitalized, for example:
see \figref{fig:example} and \tabref{tab:example}.
Figures and tables may extend across both columns to a maximum width of 17.2cm.

\begin{table}
 \begin{center}
 \begin{tabular}{|l|l|}
  \hline
  String value & Numeric value \\
  \hline
  Hello ISMIR  & 2014 \\
  \hline
 \end{tabular}
\end{center}
 \caption{Table captions should be placed below the table.}
 \label{tab:example}
\end{table}
